Visualizations for article

### 2016-05-26 101-visualizations-for-article.Rmd
Minor tweaks to colors and sizes

```{r NV1861-borrowings, fig.height=4.5}
spectrogram("NV1861", best_matches, white_list = 5)
```

@@

```{r NV1861-to-NY, fig.height=4.5}
all_NV1861 <- data_frame(borrower_code = "NV1861",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "NV1861") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

@@

```{r NY1879-matches, fig.height=7}
spectrogram("NY1879", best_matches, white_list = c("NY1853", "NY1876"))
```

>>>>

```{r NV1861-borrowings, fig.height=4}
spectrogram("NV1861", best_matches, white_list = 5)
```

@@

```{r NV1861-to-NY, fig.height=4}
all_NV1861 <- data_frame(borrower_code = "NV1861",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "NV1861") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

@@

```{r NY1879-matches, fig.height=6.5}
spectrogram("NY1879", best_matches, white_list = c("NY1853", "NY1876"))
```
